Individual and Differential Harm in Redistricting

### 2022-03-29 paper/paper.Rmd
work

First, $U^{(G)}, U^{(L)}, H$, and $\Delta H(q)$ are all averaged over possible election outcomes, and so do not suffer from discreteness.
And as discussed above, $U^{(G)}$ and $U^{(L)}$ both reward proportionality.
Of course, proportionality is not always possible, given a state's political geography.
The harm measures $H$ and $\Delta H(q)$ both reflect this by comparing to a set of counterfactual districting plans.
This addresses one inherent shortcoming of the efficiency gap, illustrated best by the state of Massachusetts.
According to the efficiency gap, Massachussetts' congressional districting plan is a Democratic gerrymander ($EG=-0.14$).
But it is impossible to draw a single Republican congressional district in the state.
Consequently $H$ and $\Delta H(q)$ are everywhere 0.

@@

```{=tex}
\begin{proof}
\end{proof}
```
# Computing Harm and Fairness from Precinct-level Election Data {#app:formulas}

>>>>

First, $U^{(G)}, U^{(L)}, H$, and $\Delta H(q)$ are all averaged over possible election outcomes, and so do not suffer from discreteness.
And as discussed above, $U^{(G)}$ and $U^{(L)}$ both reward proportionality.
Of course, proportionality is not always possible, given a state's political geography.
The harm measures $H$ and $\Delta H(q)$ both reflect this by comparing to a set of counterfactual districting plans.
This addresses one inherent shortcoming of the efficiency gap, illustrated best by the state of Massachusetts.
According to the efficiency gap, Massachusetts' congressional districting plan is a Democratic gerrymander ($EG=-0.14$).
But it is impossible to draw a single Republican congressional district in the state.
Consequently $H$ and $\Delta H(q)$ are everywhere 0.

@@

```{=tex}
\begin{proof}
\end{proof}
```
# Computing Harm Measures from Precinct-level Election Data {#app:formulas}
